---
title: "IRT"
author: "Taylor Brown"
date: "02/02/2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=TRUE, cache = FALSE}


knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(dplyr)
library(mirt)
library(naniar)
library(Rcpp)
library(haven)
library(VIM)
```

#Define data and load packages
```{r}
data<-data<-haven::read_sav("all_data_cleaned_and_mean_replaced_IRT.sav")%>%
  mutate_if(is.character, as.factor)



```

#view data and define the scale
```{r}
glimpse(data)

scale <-(data[,44:51])

head(scale, 8) 

```

#Fit the graded response model using the 'mirt' R package.
```{r}

mod1 <- (mirt(scale, 1, verbose = FALSE, itemtype = 'graded', SE = TRUE))

M2(mod1, type = "C2", calcNull = FALSE, na.rm = TRUE)

```

#Check missing values

```{r}

naniar::mcar_test(scale)

```


#Examine items fit

```{r}

itemfit(mod1, na.rm = TRUE)

```

#Examine IRT parameters 
---
(0 = non discriminative; 0.01–0.34 =
very low; 0.35–0.64 = low; 0.65–1.34 = moderate; 1.35–1.69 = high; >1.70 = very high; Baker, 2001)
---

```{r}

IRT_parms <- coef(mod1, IRTpars = TRUE, simplify = TRUE, na.rm=TRUE)
IRT_parms$items

```

#Examine Factor analysis parameters

```{r}

summary(mod1)

```

##Produce IRT plots - Category characteristic Curve

```{r plot1, echo=FALSE}

plot(mod1, type='trace', which.item = c(1,2,3,4,5,6,7,8), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
     theta_lim = c(-3, 3), 
     main = "")


```


#Item information Curve

```{r plot2, echo=FALSE}

plot(mod1, type='infotrace', which.item = c(1,2,3,4,5,6,7,8), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=1, space = 'right', cex = .8), 
     theta_lim = c(-3, 3), 
     main="")

```

#Scale informaiton and conditional standard errors

```{r plot3, echo=FALSE}

plot(mod1, type = 'infoSE', theta_lim = c(-3, 3), 
     main="")

```

#conditional reliability

```{r plot4, echo=FALSE}

plot(mod1, type = 'rxx', theta_lim = c(-3, 3), 
     main="" )

## Single IRT reliability is also produced ##

marginal_rxx(mod1)


```

#Scale characteristic Curve


```{r plot5, echo=FALSE}

plot(mod1, type = 'score', theta_lim = c(-3, 3), main = "")

```

# THE END
